Examples

### 2016-11-19 Algebra/Noetherian Ring.tex
Finding components in representation (Group theory in physics).
Learn to use multirow/column in table. Some minor modification of module notes for Algebra.

\usepackage{float}  % For H in figures
\usepackage{amsmath, amssymb} % For math
\usepackage{mathtools} % dcases*, see https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics#The_cases_environment
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage[unicode]{hyperref} % For hyperlink everything.
\usepackage{braket} 
\usepackage[T1]{fontenc}
\usepackage{listings}

\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\usepackage[all]{xy} % For drawing category diagrams
\usepackage{mathrsfs}
\usepackage{nomencl} % For a index of symbols.
\makenomenclature % For a index of symbols.
\title{Noetherian Ring}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    A note about Noetherian Ring, majorly from the book \cite{lang}.
}
\tableofcontents

\section{Module}
\label{sec:Module}
(\textbf{pp.117 to 118 of \cite{lang}})
\begin{defi}[Module]
    \nomenclature{$M$ Module}{A left module\nomrefpage.}
Let $A$: ring. $M$ is a nomen left $A$-module if and only if 
\begin{enumerate}
    \item $M$ is an abelian group, usually written additively.
    \item there exists an operation of $A$ on $M$, written as a
        multiplicative monoid, such that, for any $a,b\in A$, any
        $x,y \in M$, we have:
        \begin{align}
            (a+b) x = ax + bx\\
            a(x+y) = ax + ay
        \end{align}
\end{enumerate}
\end{defi}

@@

\begin{ex}{Examples of modules}
    \begin{enumerate}
        \item $A$ is a module over itself.
        \item Any commutative group is a $\mathbb{Z}$-module.
        \item Any left ideal of $A$ is a module over $A$, i.e. a left
            $A$-module.
        \item A vector space $V$ over $K$, is basically a $K$-module,
            with the additional structure of $K$ being a field.
        \item Let $V$ be a vector space. 
            Let $R$ be the ring of all linear maps of $V$ into itself.
            Then $V$ is also a module over $R$.
    \end{enumerate}
\end{ex}

>>>>

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

\makenomenclature % For an index of symbols.

% Show the keys for labels, replace options with "final" when done
% with editing.
\usepackage[draft,notref]{showkeys}

% For the xymatrices I created before I learn to
% use tikzcd for diagrams.
\usepackage[all]{xy}

\title{Noetherian Ring}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    A note about Noetherian Ring, majorly from the book \cite{lang}.
}
\tableofcontents

\section{Module}
\label{sec:Module}
(\textbf{pp.117 to 118 of \cite{lang}})
\begin{defi}[Module]
    \nomenclature{$M$ Module}{A left module\nomrefpage.}
Let $A$: ring. $M$ is a left $A$-module if and only if 
\begin{enumerate}
    \item $M$ is an abelian group, usually written additively.
    \item there exists an operation of $A$ on $M$, written as a
        multiplicative monoid, such that, for any $a,b\in A$, any
        $x,y \in M$, we have:
        \begin{align}
            (a+b) x = ax + bx\\
            a(x+y) = ax + ay
        \end{align}
\end{enumerate}
    This captures the notion of being \textit{linear}.
\end{defi}

@@

\begin{ex}{Examples of modules}
    \begin{enumerate}
        \item $A$ is a module over itself.
        \item Any commutative group is a $\mathbb{Z}$-module.
        \item Any left ideal of $A$ is a module over $A$, i.e. a left
            $A$-module.
        \item A vector space $V$ over $K$, is basically a $K$-module,
            with the additional structure of $K$ being a field.
        \item Let $V$ be a vector space. 
            Let $R$ be the ring of all linear maps of $V$ into itself.
            Then $V$ is also a module over $R$, since $R$ are just
            linear maps.
    \end{enumerate}
\end{ex}
\begin{ex}
    One can also pass the module structure $M$ from function whose
    codomain is $M$. For example, when $M$ is an $A$-module and $S$ is
    an nonempty set. The set of all maps $\mathrm{Map}(S,M)$ can be
    made into an $A$-module. Let $a\in A$, $a$ acts on 
    $f\in \mathrm{Map}(S,M)$ by $(af)(s) := a(f(s))$.
\end{ex}

### 2016-11-19 Draft/sections/misc-other.tex
Learn to use multirow/column in table. Some minor modification of module notes for Algebra.

\subsection{About Matlab}
\label{sec:About-Matlab}
\paragraph{On using $A/B$ or $A\\B$}
Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide}
, abbrevated $A/B$ and $A\\B$, are different and should be used with
caution. One can check that:
\begin{center}
    $A\cdot D^{-1}$ is equivalent to $A/D$, $D^{-1}\cdot A$ is
    equivalent to $D\backslash A$.
\end{center}
Also, it is straightforward to prove that the two are equal if and only if $A$ commutes with $D$.

>>>>

\subsection{About Matlab}
\label{sec:About-Matlab}
\paragraph{On using $A/B$ or $A\backslash B$}
Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide} ,
abbrevated $A/B$ and $A\backslash B$, are different and should be used
with caution. One can check that:
\begin{center}
    $A\cdot D^{-1}$ is equivalent to $A/D$, $D^{-1}\cdot A$ is
    equivalent to $D\backslash A$.
\end{center}
Also, it is straightforward to prove that the two are equal if and only if $A$ commutes with $D$.

### 2016-11-19 Latex packages/latex examples.tex
Learn to use multirow/column in table. Some minor modification of module notes for Algebra.

\begin{table}[ht]
	\centering
	\caption{Classification}
	\label{tab:classification}
	\vspace{+0.5pt}
	\rowcolors{1}{white}{lightgrey}
	\tabulinesep=1.2mm
	\begin{tabu}{  X[l] X[l] X[l] X[l] }
		\textit{Symmetry} & \textit{Spatial Dimension} &
		\textit{Result} & \textit{Other Keywords} \\
		\hline
		T & 0 & An intger: the number of particle-occupied Kramers
		doublet states & \\
		T & 1 & None & \\
		T & 2 & $\mathbb{Z}_2$ & \\
		T & 3 & $\mathbb{Z}_2$ & $3D$ crystals have additional
		$3\mathbb{Z}_2$ invariant$ \Rightarrow$ "weak topological
		insulators \\
		Q(?) & 2 & Characterized by $\mu$ in units of $e^2/h$ & TKNN \\
		Q(?) & even  d & Topological invariant ($k$-th Chern number) \\
		Q(?) & 0 &  number of single-particle states with negative
		energy ($E< E_F = 0$), which are filled with electrons. \\
		T\& Q \\
		No T \& No Q & 0 & $\mathbb{Z}_2$ \\
		No T \& No Q & 1 &$\mathbb{Z}_2$ &"majorana chain"  \\
		No T \& No Q & 2 & Topological number is integer. & Even-odd
		effects. \\
		\bottomrule
	\end{tabu}
\end{table}
\section{Anchor}
\label{sec:Anchor}

>>>>

\begin{table}[ht]
	\centering
	\caption{Classification}
	\label{tab:classification}
	\vspace{+0.5pt}
	\rowcolors{1}{white}{lightgrey}
	\tabulinesep=1.2mm
	\begin{tabu}{  X[l] X[l] X[l] X[l] }
		\textit{Symmetry} & \textit{Spatial Dimension} &
		\textit{Result} & \textit{Other Keywords} \\
		\hline
		T & 0 & An intger: the number of particle-occupied Kramers
		doublet states & \\
		T & 1 & None & \\
		T & 2 & $\mathbb{Z}_2$ & \\
		T & 3 & $\mathbb{Z}_2$ & $3D$ crystals have additional
		$3\mathbb{Z}_2$ invariant$ \Rightarrow$ "weak topological
		insulators \\
		Q(?) & 2 & Characterized by $\mu$ in units of $e^2/h$ & TKNN \\
		Q(?) & even  d & Topological invariant ($k$-th Chern number) \\
		Q(?) & 0 &  number of single-particle states with negative
		energy ($E< E_F = 0$), which are filled with electrons. \\
		T\& Q \\
		No T \& No Q & 0 & $\mathbb{Z}_2$ \\
		No T \& No Q & 1 &$\mathbb{Z}_2$ &"majorana chain"  \\
		No T \& No Q & 2 & Topological number is integer. & Even-odd
		effects. \\
		\bottomrule
	\end{tabu}
\end{table}
\textbf{Tentative Schedule:}
\begin{table}[H]
	\centering
	\caption{caption}
	\label{tab:label}
	%   \begin{tabu}{ *4c }
	\begin{tabu}{ p{15 pt} X[l] X[l] X[r] }
		$\#$ & & & Due date \\
		\hline
		\multicolumn{3}{p{\getTabuwidth}}{1. Summarise the review paper} & December, 2016 \\
		\multicolumn{3}{p{\getTabuwidth}}{2. Learn related mathematical tools (homotopy thoery, group
			cohomology, etc.)} & April, 2017 \\
		\multicolumn3{p{\getTabuwidth}}{3. Play with toy models such
			as the $1D$ quantum walk model} &
		Faburary, 2017 \\
		\multicolumn3{p{\getTabuwidth}}{4. Possible research topics:} & July, 2017 \\
		4.1 &  \multicolumn2{p{\getTabuwidth}}{classifying topological materials in new symmetry
			groups, such as the space groups;} & \multirow{4}{*}{ As above }\\
		4.2 &  \multicolumn2{p{\getTabuwidth}}{finding new ways to classify in the non-interacting picture;} & \\
		4.3 &  \multicolumn2{p{\getTabuwidth}}{experiment about the
			effectiveness of existing;} & \\
		4.4 &  \multicolumn2{p{\getTabuwidth}}{explorer approaches to the
			classification in interacting.} & \\
		\bottomrule
	\end{tabu}
\end{table}
\section{Anchor}
\label{sec:Anchor}
